### 2013-11-08 article2013.Rmd
ennen kuin aloitan semman korjaukset

**Nootti**

*Paperi on vielä hieman vaiheessa ja suosittelen tutustumaan tutkimuksen analytiikkaan osoitteessa: [http://research.muuankarski.org/attributions/](http://research.muuankarski.org/attributions/). Yritän parhaillaan saada monitasomallintamista paremmalle tolalle. Paperissa olevat mallit ovat alustavia ja pitävät sisällään sekä teoreettista että menetelmällistä epätarkkuutta.*

****

@@

![Dimensions and types of explanations of poverty](figure/nelikentta.png)

@@

![Countries used in the analysis](figure/mapplot.png)

@@

Perceived low income level  Perceived income level below the country median

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5, 
                    caption="Weighted population shares of dependent variable by country",),
              type="html",
              comment=FALSE, 
              include.rownames=FALSE,
             caption.placement="top")

@@

![World Bank's Voice and Accountability index in 2011 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_wbgi.png)

>Voice and accountability captures perceptions of the extent to which a country's citizens are able to participate in selecting their government, as well as freedom of expression, freedom of association, and a free media. [info.worldbank.org/governance/wgi/pdf/va.pdf](http://info.worldbank.org/governance/wgi/pdf/va.png)

@@

*There we some issues in converts regression outputs so the tables are evolving and can be browsed at: [http://research.muuankarski.org/attributions/code/multilevel_models.html](http://research.muuankarski.org/attributions/code/multilevel_models.html)*

****

>>>>

@@

![Dimensions and types of explanations of poverty](figure/nelikentta.pdf)

@@

![Countries used in the analysis](figure/mapplot.pdf)

@@

Perceived low income level  Perceived income level below the country median (median calculated from the 10 step scale)

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5, 
                    caption="Weighted population shares of dependent variable by country",),
              type="latex",
              comment=FALSE, 
              include.rownames=FALSE,
             caption.placement="top")

@@

![World Bank's Voice and Accountability index in 2011 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_wbgi.pdf)

>Voice and accountability captures perceptions of the extent to which a country's citizens are able to participate in selecting their government, as well as freedom of expression, freedom of association, and a free media. [info.worldbank.org/governance/wgi/pdf/va.pdf](http://info.worldbank.org/governance/wgi/pdf/va.pdf)

@@

```{rrmultilevelMultivarFullOutput, results='asis', eval=TRUE}
load("data/finalModels.RData")

model.names.multi.2 = c("Social blame vs. not",
                      "Individual blame vs. not",
                        "Social blame vs. Individual blame")

library(texreg)
texreg(list(soc.4,ind.4,socVsInc),
        naive = TRUE,
        custom.model.names = model.names.multi.2,
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
